---
title: "Stem_density_representation"
author: "Tempest McCabe"
date: "9/25/2020"
output: html_document
---

```{r}
library(rFIA)
library(rgdal)
library(sp)
library(dplyr)


```

## Loading FIA data from a state
```{r setup, include=FALSE}
states <- "GA"
full_states <- c("AL", "DE",  "FL", "GA","LA", "MD", "MS", "NC", "SC", "TN", "VA")# List of all states that intersect with the ecoregions our sites our from. Our sites are not from all of these states. Note District of columbia was excluded, for reasons i haven't diagnosed
tables <- c('PLOT', 'TREE')#, 'COND')

test <- rFIA::getFIA(states, common = TRUE, tables = tables,load = TRUE, dir = "/Users/tess/Documents/work/SERDP/", nCores = 1)
#test

## Drop columns that are only NA
plot <- test$PLOT %>% dplyr::select_if(~!all(is.na(.))) # Has lat + lon data per plot, also elevation

tree <- test$TREE  %>% dplyr::select_if(~!all(is.na(.))) # Has Diameter as DAI. IN INCHES
tree <- tree[1:6414,] # Was 1676414,   112 cutting it down for local running.  

#cond <- test$COND %>% dplyr::select_if(~!all(is.na(.))) # Has some carbon parameters like soil carbon but honestly could probably drop

# load ecoregion
eco_III_state <- sf::read_sf("/Users/tess/Documents/work/SERDP/us_eco_l3_state_boundaries/us_eco_l3_state_boundaries.shp", stringsAsFactors = FALSE) # I think eco_III$NA_L3CODE is the unique identifier I want
eco_III <- sf::read_sf("/Users/tess/Documents/work/SERDP/us_eco_l3/us_eco_l3.shp", stringsAsFactors = FALSE) # I think eco_III$NA_L3CODE is the unique identifier I want

#crs(eco_III) <- crs(sites)

ecoregions <- c("8.5.3","8.3.5")

eco_all_three <- eco_III[eco_III$NA_L3CODE %in% ecoregions,]
eco_all_three_state <- eco_III_state[eco_III_state$NA_L3CODE %in% ecoregions,]
eco_8.5 <- eco_III[eco_III$NA_L3CODE == "8.5.3",]
eco_8.3 <- eco_III[eco_III$NA_L3CODE == "8.3.5",]

sites <- sf::read_sf('/Users/tess/Documents/work/SERDP/dod-plot-locations/plot-locations.shp')

```

## Filter-out resamples (By seeing if PLOT has most recent MEAS_YR)
```{r}

## Note, in subsample, no repeat samples exist. Adding a dummy one in for testing. Works! 

#dummy <- rep("Test", dim(tree)[2])
#tree <- rbind(tree, dummy)
#tree <- rbind(tree, dummy)
#tree$PLOT[6415] <- "Tess_plot"
#tree$INVYR[6415] <- "9999"

#tree$PLOT[6416] <- "Tess_plot"
#tree$INVYR[6416] <- "99999" # Fake "resample"

tree$year_plot <- paste(tree$PLOT, tree$INVYR)
tree$is_sampled_multiple_years <- rep(NA, length(tree$INVYR) )
tree$is_max_year <- rep(NA, length(tree$INVYR) )
for( i in seq_along(tree$PLOT)){
 years <- unique(tree$INVYR[tree$PLOT == tree$PLOT[i]])
 tree$is_sampled_multiple_years[i] <- (length(years) > 1 )
 tree$is_max_year[i] <- max(years) == tree$INVYR[i]
}
tree <- tree[tree$is_max_year == TRUE, ]

```

## Sort by ecoregion. Note, this section WAS broken because I can't figure out why all the projections I'm trying are off. WAIT! It works out if I transform both to 4326 projection, and make sure LON is befor LAT. 

need to operationalise now that i've tested the function
```{r}

library(sf)
library(rlang)

## Drop old measurments
plot$year_plot <- paste(plot$PLOT, plot$INVYR)
samples_to_keep <- unique(tree$year_plot)

plot <- plot[plot$year_plot %in% samples_to_keep,]

###



#sp_test <- st_within(x = , y = eco_8.3, prepared = TRUE)

## Go through and check site locations
# cords_8.5 <- coordinates(eco_8.5)
# cords_8.3 <- coordinates(eco_8.3)
# 

# 
# plot(eco_8.5)
# points(30.930536, -82.5398736)
# 
# point_test <- point.in.polygon(30.930536, -82.5398736, plot_loc)
# point_test 
# point_test <- st_intersection(plot_loc, eco_8.3)
# point_test 
# 
# geom <- proj4string(eco_8.3)
#plot_xy <- select(plot, LAT, LON)
#plot_data <- select(plot, -LAT, -LON)

#plot_sp <- SpatialPointsDataFrame(plot_xy, plot_data, proj4string = CRS("+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
#st_crs(plot_xy) <- st_crs(eco_8.3)
#test_space <- st_within(plot.sp, eco_8.3, prepared = TRUE)

#plot.sp <- st_as_sf(plot, coords = c("LON", "LAT"), crs = 4326) # 4326 is common apparently

## Need to make seperate dataframe
plot_spots <- as.data.frame(matrix(NA, ncol = 2, nrow = length(plot$LAT)))
names(plot_spots) <- c("LON", "LAT")
plot_spots$LON <- plot$LON
plot_spots$LAT <- plot$LAT

plot.sp <- st_as_sf(plot_spots, coords = c("LON", "LAT"),crs = 4326)

# test_df <- as.data.frame(matrix(NA, ncol = 2, nrow = 3))
# names(test_df) <- c("LON", "LAT")
# test_df$LAT <- c(30.930536, 47.980536, 30.930536)
# test_df$LON <- c(-82.5398736, -82.5498736, -82.5398736)
# test_df_geom <- st_as_sf(test_df,coords = c("LON", "LAT"), crs = 4326 )
# # 
# # 
# crs <- st_crs(eco_8.5$geometry)
# test.sp <- st_as_sf(test_df_geom, coords = c("LON", "LAT"), crs = 4326) #Guessed 5070 from eco
# test.sp <- st_transform(test.sp, crs = crs)
# eco_8.5_trans <- st_transform(eco_8.5, crs = 4326)
# 
# test_space <- st_intersects(test.sp, eco_8.5_trans$geometry, prepared = TRUE)
# test_space

#library(ggplot2)
#ggplot()+
  #geom_sf(data = eco_8.5_trans$geometry) +
  #geom_sf(data =test.sp$geometry)
  
  
  
  
# test_df <- as.data.frame(matrix(NA, ncol = 2, nrow = 3))
# names(test_df) <- c("LON", "LAT")
# test_df$LAT <- c(30.930536, 47.980536, 30.930536)
# test_df$LON <- c(-82.5398736, -82.5498736, -82.5398736)
# 
# 
# crs <- st_crs(eco_8.5$geometry)
# test.sp <- st_as_sf(test_df, coords = c("LON", "LAT"), crs = 4326) #Guessed 5070 from eco
# #test.sp <- st_transform(test.sp, crs = crs)
# eco_8.5_trans <- st_transform(eco_8.5, crs = 4326)
# 
# test_space <- st_intersects(test.sp, eco_8.5_trans$geometry, prepared = TRUE)
# test_space

#library(ggplot2)
#ggplot()+
  #geom_sf(data = eco_8.5_trans$geometry) +
  #geom_sf(data =test.sp$geometry)


#plot_xy <- as.matrix(plot_xy)
# plot_loc <- sp::SpatialPointsDataFrame( coords = plot_xy, data = NA, proj4string = CRS(sp::proj4string(eco_8.3)))


eco_8.5_trans <- st_transform(eco_8.5, crs = 4326)
eco_8.3_trans <- st_transform(eco_8.3, crs = 4326)
################ 
 plot$is_in_eco_8.5 <- rep(FALSE, length(plot$LAT))
 plot$is_in_eco_8.3 <- rep(FALSE, length(plot$LAT))
indicator_8.5 <- st_intersects(plot.sp, eco_8.5_trans, prepared = TRUE)
indicator_8.3 <- st_intersects(plot.sp, eco_8.3_trans, prepared = TRUE)

for (i in seq_along(plot$LAT)) {
  indexed_8.5 <- unlist(indicator_8.5[i])
  indexed_8.3 <- unlist(indicator_8.3[i])
  
  if (!is_empty(indexed_8.5)) {
    plot$is_in_eco_8.5[i] <- TRUE
  }
  if (!is_empty(indexed_8.3)) {
    if (!is_empty(indexed_8.5)) {
      print("ERROR, a point is in both ecoregions.")
      break
    }
    plot$is_in_eco_8.3[i] <- TRUE
  }
}

plot <- plot[(plot$is_in_eco_8.3 == TRUE | plot$is_in_eco_8.5 == TRUE), ]
tree <- tree[tree$PLOT %in% plot$PLOT,] # Subset trees by plots in ecoregions
```


### Calculate density. Number of stems per area. 

```{r}
tree$plot_subplot <- paste(tree$PLOT, tree$SUBP)
tree$is_big_tree <- tree$DIA >= 5.0
unique_subplots <- unique(tree$plot_subplot)
tree$density <- rep(NA, length(tree$PLT_CN))

big_area <- pi*(48*12)^2 #Radius of 48 ft
small_area <- pi*(6.8*12)^2 #Radius of 6.8 ft

for(i in seq_along(unique_subplots)){
  subplot <- tree[tree$plot_subplot == unique_subplots[i],]
  small_trees <- subplot[subplot$is_big_tree == FALSE,] # Inches
  big_trees <- subplot[subplot$is_big_tree == FALSE,] # Inches
  
  density_big_trees <- dim(big_trees)[1]/big_area
  density_small_area <- dim(small_trees)[1]/small_area
  
  tree$density[(tree$plot_subplot == unique_subplots[i]) & (tree$is_big_tree == FALSE)] <- density_small_area
  tree$density[(tree$plot_subplot == unique_subplots[i]) & (tree$is_big_tree == TRUE)] <- density_big_trees
  
}

```

Note about sampleing from FIA database documentation: https://www.fia.fs.fed.us/library/database-documentation/urban/dbDescription/Urban%20FIADB%20User%20Guides%20Database%20Description%20ver2-0%202020_09_08.pdf

DIACurrent diameter. The current diameter, in inches, at the mother-tree level. Populated for live and standing dead trees 1.0 inch d.b.h./d.r.c. Trees with diameters ranging from 1.0-4.9 inches are measured on the 6.8-foot radius microplots. Trees with diameters 5.0 inches are measured on the 48-foot radius subplot

## Test plot. I'm going to need to do a log axis

```{r}
tmp_check <- tree[tree$density > 0, ]
ggplot() + 
  geom_hex(data = tmp_check, aes(x = tmp_check$DIA, y = tmp_check$density))

ggplot() + 
  geom_point(data = tmp_check, aes(x = tmp_check$DIA, y = tmp_check$density)) + scale_x_continuous(trans="log")


big_only <- tmp_check[tmp_check$is_big_tree == TRUE,]

ggplot() + 
  geom_hex(data = big_only, aes(x = DIA, y = density)) + scale_x_continuous(trans="log")

```


## Show range of dates this goes for





## Questions
- Did we count dead trees? I can't remember. If we didn't, I should sort those out of FIA data too. STATUSCD 1= alive, 2 = dead
- DBH in our data: is it in inches or cm?
- are the small stems to sensitive to time of sampleing? 






```


Note about sampleing from FIA database documentation: https://www.fia.fs.fed.us/library/database-documentation/urban/dbDescription/Urban%20FIADB%20User%20Guides%20Database%20Description%20ver2-0%202020_09_08.pdf

DIACurrent diameter. The current diameter, in inches, at the mother-tree level. Populated for live and standing dead trees 1.0 inch d.b.h./d.r.c. Trees with diameters ranging from 1.0-4.9 inches are measured on the 6.8-foot radius microplots. Trees with diameters 5.0 inches are measured on the 48-foot radius subplot