---
title: "R Notebook"
output: html_notebook
---
This is work I did associated with my AGU 2020 poster

## scp-ing results from geo to test-pecan
Ambient_30_short: 
  - /fs/data2/output//PEcAn_1000014817/
  - /projectnb/dietzelab/pecan.data/output//tmccabe/1000014817/out/
Drought_30_short
  - /fs/data2/output//PEcAn_1000014818/
  - /projectnb/dietzelab/pecan.data/output//tmccabe/1000014818/out/
  
Ambient_15_long: 
  - /fs/data2/output//PEcAn_1000014819/
  - /projectnb/dietzelab/pecan.data/output//tmccabe/1000014819/out/
Drought_15_long:
  - /fs/data2/output//PEcAn_1000014820/
  - /projectnb/dietzelab/pecan.data/output//tmccabe/1000014820/out/
  
15-ensemble finished first. 
scp -r tmccabe@geo.bu.edu:/projectnb/dietzelab/pecan.data/output//tmccabe/1000014819/out/ /fs/data2/output//PEcAn_1000014819/out/

Note: Getting a permissions error for writing .nc files? 
sudo chmod -R 777 /fs/data2/output//PEcAn_1000014819/

## Running met2model
```{r, echo=FALSE}
library(PEcAn.ED2)
library(ncdf4)

outfile <- "/fs/data2/output//PEcAn_1000014819/out/"
run_ids <- list.files(outfile)

for(i in seq_along(run_ids)){
  file_path <- paste(outfile,"/", run_ids[i], sep = "")
  model2netcdf.ED2(file_path, 
                   29.628444, 
                   -82.354, 
                   "2013/05/01", 
                   end_date = "2019/05/31",
                   pft_names = NULL)
  
}

# outdir = file_path
# sitelat = 29.628444 
# sitelon = -82.354 
# start_date = "2013/01/01"
# end_date = "2019/05/31"
# pft_names = NULL

outfile <- "/fs/data2/output//PEcAn_1000014820/out"
run_ids <- list.files(outfile)

for(i in seq_along(run_ids)){
  file_path <- paste(outfile,"/", run_ids[i], sep = "")
  model2netcdf.ED2(file_path, 
                   29.628444, 
                   -82.354, 
                   "2013/05/01", 
                   end_date = "2019/05/31",
                   pft_names = NULL)
  
}
```
## Restarting Sensitivity and Uncertainty analysis


```{r}
library(PEcAn.all)
bety = PEcAn.DB::betyConnect(php.config = "pecan/web/config.php")

settings_Ambient <- PEcAn.settings::read.settings("/fs/data2/output//PEcAn_1000014819/pecan.CONFIGS.xml")
#runModule.get.results(settings_Ambient)
PEcAn.uncertainty::run.sensitivity.analysis(settings_Ambient)

settings_drought <- PEcAn.settings::read.settings("/fs/data2/output//PEcAn_1000014820/pecan.CONFIGS.xml")
#runModule.get.results(settings_drought)
PEcAn.uncertainty::run.sensitivity.analysis(settings_drought)

```

## Plotting trait uncertainty Now that things are constrained!
 I am just using the lolly-pop plot
```{r}


```

## looking at if traits are different between drought vs not (ie just plot trait data)

```{r}
```

